---
title: "Overdiagnosis"
author: "Oscar J. Ponce & Eddy Lincango-Naranjo"
date: "5/18/2020"
output: github_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo=TRUE)
knitr::opts_chunk$set(dpi=900)
knitr::opts_chunk$set(fig.path = "Output Figures/", dev='svg')

library("metafor")
library("tidyverse")
library("rmarkdown")
library("magrittr")
library("forestplot")
library(DescTools)
library(lattice)
```

## Open Data
>Click any of the following links to view the documents



| Stage  |      File     |  
|:----------:|:-------------:|
| Protocol | [Prospero](https://www.crd.york.ac.uk/prospero/display_record.php?RecordID=166827)|
| Search strategy | `Shown below` (Available to download as `.CSV`: [OVID](https://github.com/ponceoscarj/Thymectomy/blob/master/1%20Search%20strategy/ovid_search.csv), [Scopus](https://github.com/ponceoscarj/Thymectomy/blob/master/1%20Search%20strategy/scopus_search.csv)) |
| Abstract screening | [References used in this stage or search results](https://github.com/ponceoscarj/Thymectomy/blob/master/Screening_results/articles_for_abstract_screening.txt) |
| Full-text screening | [References used in this stage](https://github.com/ponceoscarj/Thymectomy/blob/master/Screening_results/articles_for_fulltext_screening.txt) |
| Included studies | [References used for data extraction](https://github.com/ponceoscarj/Thymectomy/blob/master/Screening_results/included_articles.txt) |
| Raw Outcome data | [Available as `.CSV`](https://github.com/ponceoscarj/Thymectomy/blob/master/Data/thymectomy_outcomes.csv)|
| Analysis codes | [Script as `R Markdown`](https://github.com/ponceoscarj/Thymectomy/blob/master/Thymectomy_results.Rmd)|



## Analysis codes

>[Click here to view our full script available as  `R Markdown` file](https://github.com/ponceoscarj/Overdiagnosis/blob/master/Overdiagnosis.Rmd)

## Raw data

>[Click here to view our raw data available as `.CSV` file](https://github.com/ponceoscarj/Overdiagnosis/blob/master/Data/overdiagnosis_excel.csv)


```{r uploading_database, echo=FALSE, warning=FALSE, message=FALSE}
od <- read.csv("Data/overdiagnosis_excel.csv")
```

```{r cleaning, echo=FALSE, warning=FALSE, message=FALSE}
od$tumorsize[od$tumorsize=="20-Oct"] <- "10-20"

names(od)[2] <- "study"
names(od)[13] <- "sex"
names(od)[26] <- "totalparticipants"
names(od)[28] <- "imaging"
names(od)[29] <- "us"
names(od)[30] <- "tac"
names(od)[31] <- "pet"
names(od)[32] <- "mri"
names(od)[34] <- "histology"
names(od)[44] <- "uscountry"
names(od)[45] <- "popbased"

table(od$country.1)
View(od)
colnames(od)

```

```{r functions_for_analysis_figures, echo=FALSE, warning=FALSE, message=FALSE, fig.show='hide'}
round2 = function(x, n=0) {scale<-10^n; sign(x)*trunc(abs(x)*scale+0.5)/scale}

ft <- function(database){
                db <- database
                db <- escalc(measure="PFT", xi=x, ni=n, data=db)
                db <- db[order(db$yi),]
                
                db$est <-  transf.ipft(db$yi, db$n)
                db$lwr.ci <- transf.ipft(db$yi - 1.96*sqrt(db$vi), db$n)
                db$upr.ci <- transf.ipft(db$yi + 1.96*sqrt(db$vi), db$n)
                
                
                db$rate <- paste(db$x,"/",db$n)
                db$prop <- paste(formatC(db$est, format='f', digits =2)," ",
                                     "(",formatC(db$lwr.ci, format='f', digits =2),
                                     "-",formatC(db$upr.ci, format='f', digits=2),")")  
                
                ma <- rma(db$yi, db$vi, method="DL", data=db)
                exp <- predict(ma, transf=transf.ipft.hm, targs=list(ni=db$n))

      list(pre = db, ma = ma, exp = exp)
}

glmm <- function(database){
                db <- database
                ma <- rma.glmm(measure="PLO", xi=x, ni=n, 
                      data=db)
                exp <- predict(ma, transf=transf.ilogit, digits=3)   
                db$est <-  transf.ilogit(ma$yi, db$n)
                db$lwr.ci <- transf.ilogit(ma$yi - 1.96*sqrt(ma$vi), db$n)
                db$upr.ci <- transf.ilogit(ma$yi + 1.96*sqrt(ma$vi), db$n)
                db$rate <- paste(db$x,"/",db$n)
                db$prop <- paste(formatC(db$est, format='f', digits =2)," ",
                                     "(",formatC(db$lwr.ci, format='f', digits =2),
                                     "-",formatC(db$upr.ci, format='f', digits=2),")")   
                db <- db[order(db$est),]
        list(pre = db, ma = ma, exp = exp)
}

subgroup_interaction <- function(group1, group2, name1, name2){
                  
          x <- data.frame(estimate = c(coef(group1$ma), coef(group2$ma)), 
                          stderror = c(group1$ma$se, group2$ma$se),
                          meta = c(name1, name2), 
                          tau2 = round(c(group1$ma$tau2, group2$ma$tau2),3))
  
          subgroup_test <- rma(estimate, sei=stderror, mods = ~ meta, 
                               method="FE", data=x, digits=3)
}




tables_proportion_ft <- function(xi, ni, analysis,tumorsize = NA){
    ifelse(is.na(tumorsize),  
    (b <- cbind( 
        c("Author", analysis$pre$study, 
            paste("Overall proportion for", analysis$ma$k.eff, "studies","\n", 
                  "(Tau^2 = ", (formatC(analysis$ma$tau2, digits=2, format="f")), ", df = ", 
                  (analysis$ma$k - analysis$ma$p),
                  ", p ", (ifelse(analysis$ma$QEp < 0.001, 
                           paste("< 0.001"),
                           paste("= ", formatC(analysis$ma$QEp, digits=3, format="f")))),
                  "; ", "I^2", " = ", (formatC(analysis$ma$I2, digits=1, format="f")), "%)")),
        c("Frequency (n/N)",analysis$pre$rate, paste(sum(xi), " / ",
                                            sum(ni))),
        c("Prevalence (95% CI)", analysis$pre$prop, 
          paste(formatC(analysis$exp$pred, format='f', digits =2), 
           " (",formatC(analysis$exp$ci.lb, format='f', digits=2),
           "-", formatC(analysis$exp$ci.ub, format='f', digits=2), ")")))),
    (b <- cbind( 
        c("Author", analysis$pre$study, 
            paste("Overall proportion for", analysis$ma$k.eff, "studies","\n", 
                  "(Tau^2 = ", (formatC(analysis$ma$tau2, digits=2, format="f")), ", df = ", 
                  (analysis$ma$k - analysis$ma$p),
                  ", p ", (ifelse(analysis$ma$QEp < 0.001, 
                           paste("< 0.001"),
                           paste("= ", formatC(analysis$ma$QEp, digits=3, format="f")))),
                  "; ", "I^2", " = ", (formatC(analysis$ma$I2, digits=1, format="f")), "%)")),
        c("Tumor size (mm)", analysis$pre$tumorsize, NA),
        c("Frequency (n/N)",analysis$pre$rate, paste(sum(xi), " / ",
                                            sum(ni))),
        c("Prevalence (95% CI)", analysis$pre$prop, 
          paste(formatC(analysis$exp$pred, format='f', digits =2), 
           " (",formatC(analysis$exp$ci.lb, format='f', digits=2),
           "-", formatC(analysis$exp$ci.ub, format='f', digits=2), ")")))))
    
    b <- rbind(b, NA)
    b <- as_tibble(b, .name_repair = "unique")
    b <- b %>% add_row(.before = (nrow(b)-1))
    
    c <- structure(list(
    mean = c(NA,  analysis$pre$est, NA, analysis$exp$pred, NA),
    lower = c(NA,   analysis$pre$lwr.ci, NA, analysis$exp$ci.lb, NA),
    upper = c(NA,   analysis$pre$upr.ci, NA, analysis$exp$ci.ub, NA)),
    .Names = c("mean", "lower", "upper"),
    row.names = c(NA, (-1L*nrow(b))),
     class = "data.frame")

    
    list(b = b, c = c)

}


tables_proportion_glmm <- function(xi, ni, analysis, tumorsize = NA){
    ifelse(is.na(tumorsize),
    
    (b <- cbind( 
        c("Author", analysis$pre$study, 
            paste("Overall proportion for", analysis$ma$k.eff, "studies","\n", 
                  "(Tau^2 = ", (formatC(analysis$ma$tau2, digits=2, format="f")), ", df = ", 
                  (analysis$ma$k - analysis$ma$p),
                   ", p ", (ifelse(analysis$ma$QEp.Wld < 0.001, 
                           paste("< 0.001"),
                           paste("= ", formatC(analysis$ma$QEp.Wld, digits=3, format="f")))),
                  "; ", "I^2", " = ", (formatC(analysis$ma$I2, digits=1, format="f")), "%)")),
        c("Frequency (n/N)",analysis$pre$rate, paste(sum(xi), " / ",
                                            sum(ni))),
        c("Prevalence (95% CI)", analysis$pre$prop, 
          paste(formatC(analysis$exp$pred, format='f', digits =2), 
           " (",formatC(analysis$exp$ci.lb, format='f', digits=2),
           "-", formatC(analysis$exp$ci.ub, format='f', digits=2), ")")))),
    (b <- cbind( 
        c("Author", analysis$pre$study, 
            paste("Overall proportion for", analysis$ma$k.eff, "studies","\n", 
                  "(Tau^2 = ", (formatC(analysis$ma$tau2, digits=2, format="f")), ", df = ", 
                  (analysis$ma$k - analysis$ma$p),
                   ", p ", (ifelse(analysis$ma$QEp.Wld < 0.001, 
                           paste("< 0.001"),
                           paste("= ", formatC(analysis$ma$QEp.Wld, digits=3, format="f")))),
                  "; ", "I^2", " = ", (formatC(analysis$ma$I2, digits=1, format="f")), "%)")),
        c("Tumor size (mm)", analysis$pre$tumorsize, NA),
        c("Frequency (n/N)",analysis$pre$rate, paste(sum(xi), " / ",
                                            sum(ni))),
        c("Prevalence (95% CI)", analysis$pre$prop, 
          paste(formatC(analysis$exp$pred, format='f', digits =2), 
           " (",formatC(analysis$exp$ci.lb, format='f', digits=2),
           "-", formatC(analysis$exp$ci.ub, format='f', digits=2), ")")))))
    
    b <- rbind(b, NA)
    b <- as_tibble(b, .name_repair = "unique")
    b <- b %>% add_row(.before = (nrow(b)-1))
    
    c <- structure(list(
    mean = c(NA,  analysis$pre$est, NA, analysis$exp$pred, NA),
    lower = c(NA,   analysis$pre$lwr.ci, NA, analysis$exp$ci.lb, NA),
    upper = c(NA,   analysis$pre$upr.ci, NA, analysis$exp$ci.ub, NA)),
    .Names = c("mean", "lower", "upper"),
    row.names = c(NA, (-1L*nrow(b))),
     class = "data.frame")

    
    list(b = b, c = c)

}



plot_individual_proportion_ft <- function(words, numbers, sizebox, box_ma_results, overall_box){
  
    box_size <- (sizebox*(weights(box_ma_results)))

    forestplot(words,
               graph.pos = ncol(words),
               zero = NA,
               numbers,
               new_page = TRUE,
               colgap = unit(5, "mm"),
               hrzl_lines = list("2" = gpar (lwd=1, columns=c(1:4), col="black")),
               lineheight=unit(0.5,'cm'),
               boxsize = c(NA, box_size, NA, overall_box, NA),
               line.margin = 2,
               is.summary = c(T, rep(F, nrow(words)-3), T, F),
               align = c("l","c"),
               ci.vertices = TRUE,
               txt_gp = fpTxtGp(label =gpar (cex=0.8), 
                                ticks = gpar(cex = 0.8, fontface="bold"),
                                summary = gpar(cex = 0.8),
                                xlab = gpar(cex=0.8)),
               xticks = c(0, 0.1, 0.2, 0.3, 0.4,0.5, 0.6, 0.7, 0.8, 0.9, 1),
               xlog=FALSE,
               clip = c(0,  0.4),
               grid = gpar(lty=3, col="gray"),
               lwd.xaxis = 1,
               lwd.ci = 2.2,
               graphwidth = unit(10,"cm"),
               col=fpColors(box="black",line="grey", axes="grey20", summary="black"))
}




plot_individual_proportion_glmm <- function(words, numbers, ind_box, overall_box){

forestplot(words,
           graph.pos = ncol(words),
           zero = NA,
           numbers,
           new_page = TRUE,
           colgap = unit(5, "mm"),
           hrzl_lines = list("2" = gpar (lwd=1, columns=c(1:4), col="black")),
           lineheight=unit(0.5,'cm'),
           line.margin = 2,
           boxsize = c(rep(ind_box, nrow(words)-2), overall_box, NA),
           is.summary = c(T, rep(F, nrow(words)-3), T, F),
           align = c("l","c"),
           ci.vertices = TRUE,
           txt_gp = fpTxtGp(label =gpar (cex=0.8), 
                            ticks = gpar(cex = 0.8, fontface="bold"),
                            summary = gpar(cex = 0.8),
                            xlab = gpar(cex=0.8)),
           xticks = c(0, 0.1, 0.2, 0.3, 0.4,0.5, 0.6, 0.7, 0.8, 0.9, 1),
           xlog=FALSE,
           clip = c(0,  0.4),
           grid = gpar(lty=3, col="gray"),
           lwd.xaxis = 1,
           lwd.ci = 2.2,
           graphwidth = unit(10,"cm"),
           col=fpColors(box="black",line="grey", axes="grey20", summary="black"))

}  

extract_info_maft_proportions <- function(group, maresults, subgroup = NA, sub_analysis){
  ifelse(is.na(subgroup),
  a <- c(paste(group),
    maresults$ma[[15]],
    sum(maresults$pre$x),
    sum(maresults$pre$n),
    maresults$ma[[25]],
    maresults$exp[[1]], 
    maresults$exp[[3]], 
    maresults$exp[[4]],
    NA),
  a <- c(paste(group),
    maresults$ma[[15]],
    sum(maresults$pre$x),
    sum(maresults$pre$n),
    maresults$ma[[25]],
    maresults$exp[[1]], 
    maresults$exp[[3]], 
    maresults$exp[[4]],
    sub_analysis[[24]]))
  
  return(a)
}


extract_info_maglmm_proportions <- function(group, maresults, subgroup = NA, sub_analysis){
  ifelse(is.na(subgroup),
  a <- c(paste(group),
    maresults$ma[[15]],
    sum(maresults$pre$x),
    sum(maresults$pre$n),
    maresults$ma[[28]],
    maresults$exp[[1]], 
    maresults$exp[[3]], 
    maresults$exp[[4]],
    NA),
  a <- c(paste(group),
    maresults$ma[[15]],
    sum(maresults$pre$x),
    sum(maresults$pre$n),
    maresults$ma[[28]],
    maresults$exp[[1]], 
    maresults$exp[[3]], 
    maresults$exp[[4]],
    sub_analysis[[24]]))
  
  return(a)
}



```

```{r analysis_incidental, echo=FALSE, message=FALSE, warning=FALSE} 

od1 <- od
names(od1)[names(od1) == "inc"] <- "x"
names(od1)[names(od1) == "totalparticipants"] <- "n"


inc_overall <- subset(od1, overall=="Yes" & !is.na(x))
inc1 <- ft(inc_overall)
inc2 <- glmm(inc_overall)

inc_male <- subset(od1, sex=="Male" & !is.na(x))
inc3 <- ft(inc_male)
inc4 <- glmm(inc_male)

inc_female <- subset(od1, sex=="Female" & !is.na(x))
inc5 <- ft(inc_female)
inc6 <- glmm(inc_female)

inc_sex_ft <- subgroup_interaction(inc3, inc5, "Male", "Female")
inc_sex_glmm <- subgroup_interaction(inc4, inc6, "Male", "Female")


inc_more45 <- subset(od1, age2==">45" & !is.na(x))
inc7 <- ft(inc_more45)
#not feasible, only 1 study
#inc8 <- glmm(inc_more45)

inc_less45 <- subset(od1, age2=="<45" & !is.na(x))
inc9 <- ft(inc_less45)
#not feasible, only 1 study
#i10 <- glmm(inc_less45)

inc_age_ft <- subgroup_interaction(inc7, inc9, ">45", "<45")


inc_more10 <- subset(od1, tumor1==">10" & !is.na(x))
inc11 <- ft(inc_more10)
inc12 <- glmm(inc_more10)

inc_less10 <- subset(od1, tumor1=="<10" & !is.na(x))
inc13 <- ft(inc_less10)
inc14 <- glmm(inc_less10)

inc_tumorsize_ft <- subgroup_interaction(inc11, inc13, ">10", "<10")
inc_tumorsize_glmm <- subgroup_interaction(inc12, inc14, ">10", "<10")


inc_usa <- subset(od1, uscountry=="USA" & overall=="Yes" & !is.na(x))
inc15 <- ft(inc_usa)
inc16 <- glmm(inc_usa)

inc_nonusa <- subset(od1, uscountry=="non-USA" & overall=="Yes" & !is.na(x))
inc17 <- ft(inc_nonusa)
inc18 <- glmm(inc_nonusa)

inc_uscountry_ft <- subgroup_interaction(inc15, inc17, "USA", "non-USA")
inc_uscountry_glmm <- subgroup_interaction(inc16, inc18, "USA", "non-USA")


inc_pop <- subset(od1, popbased=="Population based studies" & overall=="Yes" & !is.na(x))
inc19 <- ft(inc_pop)
inc20 <- glmm(inc_pop)

inc_nonpop <- subset(od1, popbased=="Non-population based studies" & overall=="Yes" 
                   & !is.na(x))
inc21 <- ft(inc_nonpop)
inc22 <- glmm(inc_nonpop)

inc_popbased_ft <- subgroup_interaction(inc19, inc21, "Population based", "Non-population based")
inc_popbased_glmm <- subgroup_interaction(inc20, inc22, "Population based", "Non-population based")

```

```{r analysis_imaging, echo=FALSE, message=FALSE, warning=FALSE} 


od2 <- od
names(od2)[names(od2) == "imaging"] <- "x"
names(od2)[names(od2) == "totalparticipants"] <- "n"

i_overall <- subset(od2, overall=="Yes" & !is.na(x))
i1 <- ft(i_overall)
i2 <- glmm(i_overall)

i_male <- subset(od2, sex=="Male" & !is.na(x))
i3 <- ft(i_male)
i4 <- glmm(i_male)

i_female <- subset(od2, sex=="Female" & !is.na(x))
i5 <- ft(i_female)
i6 <- glmm(i_female)

i_sex_ft <- subgroup_interaction(i3, i5, "Male", "Female")
i_sex_glmm <- subgroup_interaction(i4, i6, "Male", "Female")


i_more45 <- subset(od2, age2==">45" & !is.na(x))
i7 <- ft(i_more45)
#not feasible, only 1 study
#i8 <- glmm(i_more45)

i_less45 <- subset(od2, age2=="<45" & !is.na(x))
i9 <- ft(i_less45)
#not feasible, only 1 study
#i10 <- glmm(i_less45)

i_age_ft <- subgroup_interaction(i7, i9, ">45", "<45")


i_more10 <- subset(od2, tumor1==">10" & !is.na(x))
i11 <- ft(i_more10)
i12 <- glmm(i_more10)

i_less10 <- subset(od2, tumor1=="<10" & !is.na(x))
i13 <- ft(i_less10)
i14 <- glmm(i_less10)

i_tumorsize_ft <- subgroup_interaction(i11, i13, ">10", "<10")
i_tumorsize_glmm <- subgroup_interaction(i12, i14, ">10", "<10")


i_usa <- subset(od2, uscountry=="USA" & overall=="Yes" & !is.na(x))
i15 <- ft(i_usa)
i16 <- glmm(i_usa)

i_nonusa <- subset(od2, uscountry=="non-USA" & overall=="Yes" & !is.na(x))
i17 <- ft(i_nonusa)
i18 <- glmm(i_nonusa)

i_uscountry_ft <- subgroup_interaction(i15, i17, "USA", "non-USA")
i_uscountry_glmm <- subgroup_interaction(i16, i18, "USA", "non-USA")


i_pop <- subset(od2, popbased=="Population based studies" & overall=="Yes" & !is.na(x))
i19 <- ft(i_pop)
i20 <- glmm(i_pop)

i_nonpop <- subset(od2, popbased=="Non-population based studies" & overall=="Yes" 
                   & !is.na(x))
i21 <- ft(i_nonpop)
i22 <- glmm(i_nonpop)

i_popbased_ft <- subgroup_interaction(i19, i21, "Population based", "Non-population based")
i_popbased_glmm <- subgroup_interaction(i20, i22, "Population based", "Non-population based")

```

```{r analysis_us, echo=FALSE, message=FALSE, warning=FALSE} 

us_overall <- subset(od, overall=="Yes" & !is.na(us))
names(us_overall)[names(us_overall) == "us"] <- "x"
names(us_overall)[names(us_overall) == "totalparticipants"] <- "n"

us1 <- ft(us_overall)
us2 <- glmm(us_overall)

```


```{r analysis_tac, echo=FALSE, message=FALSE, warning=FALSE} 
tac_overall <- subset(od, overall=="Yes" & !is.na(tac))
names(tac_overall)[names(tac_overall) == "tac"] <- "x"
names(tac_overall)[names(tac_overall) == "totalparticipants"] <- "n"

tac1 <- ft(tac_overall)
tac2 <- glmm(tac_overall)

```

```{r analysis_pet, echo=FALSE, message=FALSE, warning=FALSE} 
pet_overall <- subset(od, overall=="Yes" & !is.na(pet))
names(pet_overall)[names(pet_overall) == "pet"] <- "x"
names(pet_overall)[names(pet_overall) == "totalparticipants"] <- "n"

pet1 <- ft(pet_overall)
pet2 <- glmm(pet_overall)

```

```{r analysis_mri, echo=FALSE, message=FALSE, warning=FALSE} 
mri_overall <- subset(od, overall=="Yes" & !is.na(mri))
names(mri_overall)[names(mri_overall) == "mri"] <- "x"
names(mri_overall)[names(mri_overall) == "totalparticipants"] <- "n"

mri1 <- ft(mri_overall)
mri2 <- glmm(mri_overall)

```



```{r analysis_histology, echo=FALSE, message=FALSE, warning=FALSE} 

od3 <- od
names(od3)[names(od3) == "histology"] <- "x"
names(od3)[names(od3) == "totalparticipants"] <- "n"

hist_overall <- subset(od3, overall=="Yes" & !is.na(x))
hist1 <- ft(hist_overall)
hist2 <- glmm(hist_overall)

hist_male <- subset(od3, sex=="Male" & !is.na(x))
hist3 <- ft(hist_male)
hist4 <- glmm(hist_male)

hist_female <- subset(od3, sex=="Female" & !is.na(x))
hist5 <- ft(hist_female)
hist6 <- glmm(hist_female)

hist_sex_ft <- subgroup_interaction(hist3, hist5, "Male", "Female")
hist_sex_glmm <- subgroup_interaction(hist4, hist6, "Male", "Female")


hist_more45 <- subset(od3, age2==">45" & !is.na(x))
hist7 <- ft(hist_more45)
#not feasible, only 1 study
#hist8 <- glmm(hist_more45)

hist_less45 <- subset(od3, age2=="<45" & !is.na(x))
hist9 <- ft(hist_less45)
#not feasible, only 1 study
#i10 <- glmm(hist_less45)

hist_age_ft <- subgroup_interaction(hist7, hist9, ">45", "<45")


hist_more10 <- subset(od3, tumor1==">10" & !is.na(x))
hist11 <- ft(hist_more10)
hist12 <- glmm(hist_more10)

hist_less10 <- subset(od3, tumor1=="<10" & !is.na(x))
hist13 <- ft(hist_less10)
hist14 <- glmm(hist_less10)

hist_tumorsize_ft <- subgroup_interaction(i11, i13, ">10", "<10")
hist_tumorsize_glmm <- subgroup_interaction(i12, i14, ">10", "<10")


hist_usa <- subset(od3, uscountry=="USA" & overall=="Yes" & !is.na(x))
hist15 <- ft(hist_usa)
hist16 <- glmm(hist_usa)

hist_nonusa <- subset(od3, uscountry=="non-USA" & overall=="Yes" & !is.na(x))
hist17 <- ft(hist_nonusa)
hist18 <- glmm(hist_nonusa)

hist_uscountry_ft <- subgroup_interaction(hist15, hist17, "USA", "non-USA")
hist_uscountry_glmm <- subgroup_interaction(hist16, hist18, "USA", "non-USA")


hist_pop <- subset(od3, popbased=="Population based studies" & overall=="Yes" & !is.na(x))
hist19 <- ft(hist_pop)
hist20 <- glmm(hist_pop)

hist_nonpop <- subset(od3, popbased=="Non-population based studies" & overall=="Yes" 
                   & !is.na(x))
hist21 <- ft(hist_nonpop)
hist22 <- glmm(hist_nonpop)

hist_popbased_ft <- subgroup_interaction(hist19, hist21, "Population based", "Non-population based")
hist_popbased_glmm <- subgroup_interaction(hist20, hist22, "Population based", "Non-population based")

```

# Summary of forest plots 

## Figure 1. Incidental diagnosis in patients with Thyroid Cancer by population group
> To generate this forest plot, we used information from Supplementary Figures 1 to 30.

```{r summary_overall_forestplots, echo=FALSE, fig.height=7, fig.width=12, message=FALSE, warning=FALSE}

x <- rbind(
  c( "subgroup", "studies", "n", "N", "i2", "est", "llci", "ulci", "p"),
  c(NA),
  extract_info_maft_proportions("Overall", inc1),
  c(NA),
  c("by Method of Diagnosis", rep(NA, 8)),
  extract_info_maft_proportions("Imaging", i1),
  extract_info_maft_proportions("Ultrasound", us1),
  extract_info_maft_proportions("CT scan", tac1),
  extract_info_maft_proportions("MRI", mri1),
  extract_info_maft_proportions("PET", pet1),
  extract_info_maft_proportions("Histology", hist1),
  c(NA),
  c("by Subgroups", rep(NA, 8)),
  c("Sex", rep(NA, 8)),
  extract_info_maft_proportions("Male", inc3, subgroup = T, sub_analysis = inc_sex_ft),
  extract_info_maft_proportions("Female", inc5),
  c("Age", rep(NA, 8)),
  extract_info_maft_proportions(">45y", inc7, subgroup = T, sub_analysis = inc_age_ft),
  extract_info_maft_proportions("<45y", inc9),
  c("Tumor size", rep(NA, 8)),
  extract_info_maft_proportions(">10mm", inc11, subgroup = T, sub_analysis = inc_tumorsize_ft),
  extract_info_maft_proportions("<10mm", inc13),
  c("USA-based", rep(NA, 8)),
  extract_info_maft_proportions("USA", inc15, subgroup = T, sub_analysis = inc_uscountry_ft),
  extract_info_maft_proportions("non-USA", inc17),
  c("Population-based", rep(NA, 8)),
  extract_info_maft_proportions("Population", inc19, subgroup = T, sub_analysis = inc_popbased_ft),
  extract_info_maft_proportions("non-Population", inc21),
  c(NA)
  )



colnames(x) <- x[1,]
x <- x[-1, ]
x <- as_tibble(x)
x$rate <- ifelse(is.na(x$n),
                 NA,
                 paste(x$n, "/", x$N))

x[c(2:9)] <- sapply(x[c(2:9)],as.numeric)
x$pr <- ifelse(is.na(x$est),
               NA,
              paste(formatC(x$est, format="f", digits =2), 
              "(", formatC(x$llci, format="f", digits =2),
              "-",
              formatC(x$ulci, format='f', digits=2),")"))

x$i2 <- ifelse(x$studies == 1, 
               paste("na"),
               paste(round2(x$i2, n=0),"%"))

x$p <- ifelse (is.na(x$p),
              NA, 
              ifelse(x$p<0.001, paste("<0.001"), formatC(x$p, format="f", digits =3)))


prevalence <- cbind(
  c("Population",  x$subgroup),
  c("N of studies", x$studies),
  c("Frequency (n/N)", x$rate),
  c("I^2",  x$i2),
  c("Prevalence (95% CI)", x$pr),
  c("p value",  x$p))

sub1 <- c(6, 11, 14,17, 20, 23, 26) 
prevalence[,1][sub1] <- paste("  ",prevalence[,1][sub1]) 

sub2 <- c(7:10, 15,16, 18,19, 21,22, 24,25, 27,28)
prevalence[,1][sub2] <- paste("     ",prevalence[,1][sub2]) 

rrsprev <- structure(list(
  mean = c(NA, x$est),
  lower = c(NA, x$llci),
  upper = c(NA, x$ulci)),
  .Names = c("mean", "lower", "upper"),
  row.names = c(NA, -29L),
  class = "data.frame")


x <- x %>% add_row(.before = 1)

x$box <- ifelse(x$N<=1000, 1, 
                ifelse(x$N>1000 & x$N <= 2000, 2,
                ifelse(x$N>2000 & x$N <= 3000, 3,
                ifelse(x$N>3000 & x$N <= 4000, 4,
                ifelse(x$N>4000 & x$N <= 5000, 5, NA)))))

box <- x$box*0.2

forestplot(prevalence,
               graph.pos = 5,
               zero = NA,
               rrsprev,
               new_page = TRUE,
               colgap = unit(5, "mm"),
               hrzl_lines = list("2" = gpar (lwd=1, columns=c(1:7), col="black")),
               lineheight=unit(0.5,'cm'),
               boxsize = box,
               line.margin = 2,
               is.summary = c(T,F,F,F,
                              T, rep(F, 7),
                              T, 
                              rep(c(T,F,F), 5),
                              F),
               align = c("l","c", "c", "c"),
               ci.vertices = TRUE,
               txt_gp = fpTxtGp(label =gpar (cex=0.8), 
                                ticks = gpar(cex = 0.8, fontface="bold"),
                                summary = gpar(cex = 0.8),
                                xlab = gpar(cex=0.8)),
               xticks = c(0, 0.1, 0.2, 0.3, 0.4,0.5, 0.6, 0.7, 0.8, 0.9, 1),
               xlog=FALSE,
               clip = c(0,  0.4),
               grid = gpar(lty=3, col="gray"),
               lwd.xaxis = 1,
               lwd.ci = 2.2,
               graphwidth = unit(10,"cm"),
               col=fpColors(box="black",line="grey", axes="grey20", summary="black"))




```


## Figure 2. Imaging and Histological Incidental diagnosis in patients with Thyroid Cancer by population group
> To generate this forest plot, we used information from Supplementary Figures 1 to 30.

```{r summary_Imaging_Histological_forestplots, echo=FALSE, fig.height=10, fig.width=12, message=FALSE, warning=FALSE}

x <- rbind(
  c( "subgroup", "studies", "n", "N", "i2", "est", "llci", "ulci", "p"),
  c(NA),
  extract_info_maft_proportions("Imaging - Overall", i1),
  c(NA),
  c("Subgroups", rep(NA, 8)),
  c("Sex", rep(NA, 8)),
  extract_info_maft_proportions("Male", i3, subgroup = T, sub_analysis = i_sex_ft),
  extract_info_maft_proportions("Female", i5),
  c("Age", rep(NA, 8)),
  extract_info_maft_proportions(">45y", i7, subgroup = T, sub_analysis = i_age_ft),
  extract_info_maft_proportions("<45y", i9),
  c("Tumor size", rep(NA, 8)),
  extract_info_maft_proportions(">10mm", i11, subgroup = T, sub_analysis = i_tumorsize_ft),
  extract_info_maft_proportions("<10mm", i13),
  c("USA-based", rep(NA, 8)),
  extract_info_maft_proportions("USA", i15, subgroup = T, sub_analysis = i_uscountry_ft),
  extract_info_maft_proportions("non-USA", i17),
  c("Population-based", rep(NA, 8)),
  extract_info_maft_proportions("Population", i19, subgroup = T, sub_analysis = i_popbased_ft),
  extract_info_maft_proportions("non-Population", i21),
  c(NA),
  
  
  c(NA),
  extract_info_maft_proportions("Histology - Overall", hist1),
  c(NA),
  c("Subgroups", rep(NA, 8)),
  c("Sex", rep(NA, 8)),
  extract_info_maft_proportions("Male", hist3, subgroup = T, sub_analysis = hist_sex_ft),
  extract_info_maft_proportions("Female", hist5),
  c("Age", rep(NA, 8)),
  extract_info_maft_proportions(">45y", hist7, subgroup = T, sub_analysis = hist_age_ft),
  extract_info_maft_proportions("<45y", hist9),
  c("Tumor size", rep(NA, 8)),
  extract_info_maft_proportions(">10mm", hist11, subgroup = T, sub_analysis = hist_tumorsize_ft),
  extract_info_maft_proportions("<10mm", hist13),
  c("USA-based", rep(NA, 8)),
  extract_info_maft_proportions("USA", hist15, subgroup = T, sub_analysis = hist_uscountry_ft),
  extract_info_maft_proportions("non-USA", hist17),
  c("Population-based", rep(NA, 8)),
  extract_info_maft_proportions("Population", hist19, subgroup = T, 
                                sub_analysis = hist_popbased_ft),
  extract_info_maft_proportions("non-Population", hist21),
  c(NA)
  )

colnames(x) <- x[1,]
x <- x[-1, ]
x <- as_tibble(x)
x$rate <- ifelse(is.na(x$n),
                 NA,
                 paste(x$n, "/", x$N))

x[c(2:9)] <- sapply(x[c(2:9)],as.numeric)
x$pr <- ifelse(is.na(x$est),
               NA,
              paste(formatC(x$est, format="f", digits =2), 
              "(", formatC(x$llci, format="f", digits =2),
              "-",
              formatC(x$ulci, format='f', digits=2),")"))

x$i2 <- ifelse(x$studies == 1, 
               paste("na"),
               paste(round2(x$i2, n=0),"%"))

x$p <- ifelse (is.na(x$p),
              NA, 
              ifelse(x$p<0.001, paste("<0.001"), formatC(x$p, format="f", digits =3)))


prevalence <- cbind(
  c("Population",  x$subgroup),
  c("N of studies", x$studies),
  c("Frequency (n/N)", x$rate),
  c("I^2",  x$i2),
  c("Prevalence (95% CI)", x$pr),
  c("p value",  x$p))

sub1 <- c(6, 9, 12, 15, 18, 26, 29, 32, 35, 38)
prevalence[,1][sub1] <- paste("  ",prevalence[,1][sub1]) 

sub2 <- c(7, 8, 10, 11, 13, 14, 16, 17, 19, 20,
          27, 28, 30, 31, 33, 34, 36, 37, 39, 40)
prevalence[,1][sub2] <- paste("     ",prevalence[,1][sub2]) 

rrsprev <- structure(list(
  mean = c(NA, x$est),
  lower = c(NA, x$llci),
  upper = c(NA, x$ulci)),
  .Names = c("mean", "lower", "upper"),
  row.names = c(NA, -41L),
  class = "data.frame")


x <- x %>% add_row(.before = 1)

x$box <- ifelse(x$N<=1000, 1, 
                ifelse(x$N>1000 & x$N <= 2000, 2,
                ifelse(x$N>2000 & x$N <= 3000, 3,
                ifelse(x$N>3000 & x$N <= 4000, 4,
                ifelse(x$N>4000 & x$N <= 5000, 5, NA)))))

box <- x$box*0.2

forestplot(prevalence,
               graph.pos = 5,
               zero = NA,
               rrsprev,
               new_page = TRUE,
               colgap = unit(5, "mm"),
               hrzl_lines = list("2" = gpar (lwd=1, columns=c(1:7), col="black")),
               lineheight=unit(0.5,'cm'),
               boxsize = box,
               line.margin = 2,
               is.summary = c(T,F,F,F,
                              T, 
                              rep(c(T,F,F), 5),
                              F, F, F, F,
                              T, 
                              rep(c(T,F,F), 5),
                              F),
               align = c("l","c", "c", "c"),
               ci.vertices = TRUE,
               txt_gp = fpTxtGp(label =gpar (cex=0.8), 
                                ticks = gpar(cex = 0.8, fontface="bold"),
                                summary = gpar(cex = 0.8),
                                xlab = gpar(cex=0.8)),
               xticks = c(0, 0.1, 0.2, 0.3, 0.4,0.5, 0.6, 0.7, 0.8, 0.9, 1),
               xlog=FALSE,
               clip = c(0,  0.4),
               grid = gpar(lty=3, col="gray"),
               lwd.xaxis = 1,
               lwd.ci = 2.2,
               graphwidth = unit(10,"cm"),
               col=fpColors(box="black",line="grey", axes="grey20", summary="black"))




```




# Supplementary Figures 


## Suppl. Figures using Freeman-Tukey (FT) analysis 

> Overall incidental diagnosis

<details><summary> Suppl. Figure 1: (FT) Frequency of Incidental diagnosis in patients with TC </summary>
<p>
```{r ft_incidental_overall, echo=FALSE, fig.height=6, fig.width=12, message=FALSE, warning=FALSE} 

tinc1 <- tables_proportion_ft(xi = inc1$pre$x, 
                              ni = inc1$pre$n,
                              analysis = inc1)

plot_individual_proportion_ft(words = tinc1$b,
                              numbers = tinc1$c,
                              sizebox = 0.08,
                              box_ma_results = inc1$ma,
                              overall_box = 1)
```
</p>
</details>


<details><summary> Suppl. Figure 2: (FT) Frequency of Incidental diagnosis in Male patients with TC </summary>
<p>
```{r ft_incidental_male, echo=FALSE, fig.height=4, fig.width=12, message=FALSE, warning=FALSE}
tinc3 <- tables_proportion_ft(xi = inc3$pre$x, 
                              ni = inc3$pre$n,
                              analysis = inc3)

plot_individual_proportion_ft(words = tinc3$b,
                              numbers = tinc3$c,
                              sizebox = 0.04,
                              box_ma_results = inc3$ma,
                              overall_box = 1)
```
</p>
</details>


<details><summary> Suppl. Figure 3: (FT) Frequency of Incidental diagnosis in Female patients with TC </summary>
<p>
```{r ft_incidental_female, echo=FALSE, fig.height=3, fig.width=12, message=FALSE, warning=FALSE}
tinc5 <- tables_proportion_ft(xi = inc5$pre$x, 
                              ni = inc5$pre$n,
                              analysis = inc5)

plot_individual_proportion_ft(words = tinc5$b,
                              numbers = tinc5$c,
                              sizebox = 0.040,
                              box_ma_results = inc5$ma,
                              overall_box = 1)
```
</p>
</details>


<details><summary> Suppl. Figure 4: (FT) Frequency of Incidental diagnosis in patients with TC and  tumor size >10mm </summary>
<p>
```{r ft_incidental_greater10, echo=FALSE, fig.height=3, fig.width=12, message=FALSE, warning=FALSE}
tinc11 <- tables_proportion_ft(xi = inc11$pre$x, 
                              ni = inc11$pre$n,
                              analysis = inc11,
                              tumorsize = TRUE)

plot_individual_proportion_ft(words = tinc11$b,
                              numbers = tinc11$c,
                              sizebox = 0.040,
                              box_ma_results = inc11$ma,
                              overall_box = 1)
```
</p>
</details>

  
<details><summary> Suppl. Figure 5: (FT) Frequency of Incidental diagnosis in patients with TC and tumor size <10mm </summary>
<p>
```{r ft_incidental_less10, echo=FALSE, fig.height=3, fig.width=12, message=FALSE, warning=FALSE}
tinc13 <- tables_proportion_ft(xi = inc13$pre$x, 
                              ni = inc13$pre$n,
                              analysis = inc13,
                              tumorsize = TRUE)

plot_individual_proportion_ft(words = tinc13$b,
                              numbers = tinc13$c,
                              sizebox = 0.040,
                              box_ma_results = inc13$ma,
                              overall_box = 1.5)
```
</p>
</details>


<details><summary> Suppl. Figure 6: (FT) Frequency of Incidental diagnosis in patients with TC from the USA </summary>
<p>
```{r ft_incidental_USA, echo=FALSE, fig.height=3, fig.width=12, message=FALSE, warning=FALSE}
tinc15 <- tables_proportion_ft(xi = inc15$pre$x, 
                              ni = inc15$pre$n,
                              analysis = inc15)

plot_individual_proportion_ft(words = tinc15$b,
                              numbers = tinc15$c,
                              sizebox = 0.040,
                              box_ma_results = inc15$ma,
                              overall_box = 1)
```
</p>
</details>


<details><summary> Suppl. Figure 7: (FT) Frequency of Incidental diagnosis in patients with TC from a non-USA country </summary>
<p>
```{r ft_incidental_nonUSA, echo=FALSE, fig.height=3, fig.width=12, message=FALSE, warning=FALSE}
tinc17 <- tables_proportion_ft(xi = inc17$pre$x, 
                              ni = inc17$pre$n,
                              analysis = inc17)

plot_individual_proportion_ft(words = tinc17$b,
                              numbers = tinc17$c,
                              sizebox = 0.040,
                              box_ma_results = inc17$ma,
                              overall_box = 1)

```
</p>
</details>


<details><summary> Suppl. Figure 8: (FT) Frequency of Incidental diagnosis in patients with TC from population based studies </summary>
<p>
```{r ft_incidental_pop, echo=FALSE, fig.height=3, fig.width=12, message=FALSE, warning=FALSE}
tinc19 <- tables_proportion_ft(xi = inc19$pre$x, 
                              ni = inc19$pre$n,
                              analysis = inc19)

plot_individual_proportion_ft(words = tinc19$b,
                              numbers = tinc19$c,
                              sizebox = 0.015,
                              box_ma_results = inc19$ma,
                              overall_box = 1.5)
```
</p>
</details>


<details><summary> Suppl. Figure 9: (FT) Frequency of Incidental diagnosis in patients with TC from non-population-based studies </summary>
<p>
```{r ft_incidental_nonpop, echo=FALSE, fig.height=6, fig.width=12, message=FALSE, warning=FALSE}
tinc21 <- tables_proportion_ft(xi = inc21$pre$x, 
                              ni = inc21$pre$n,
                              analysis = inc21)

plot_individual_proportion_ft(words = tinc21$b,
                              numbers = tinc21$c,
                              sizebox = 0.040,
                              box_ma_results = inc21$ma,
                              overall_box = 1)
```
</p>
</details>


<br />

> Imaging incidental diagnosis 


<details><summary> Suppl. Figure 10: (FT) Frequency of Incidental diagnosis in patients with TC </summary>
<p>
```{r ft_imaging_overall, echo=FALSE, fig.height=4, fig.width=12, message=FALSE, warning=FALSE} 

ti1 <- tables_proportion_ft(xi = i1$pre$x, 
                              ni = i1$pre$n,
                              analysis = i1)

plot_individual_proportion_ft(words = ti1$b,
                              numbers = ti1$c,
                              sizebox = 0.05,
                              box_ma_results = i1$ma,
                              overall_box = 1)
```
</p>
</details>


<details><summary> Suppl. Figure 11: (FT) Frequency of Incidental imaging diagnosis in Male patients with TC </summary>
<p>
```{r ft_imaging_male, echo=FALSE, fig.height=4, fig.width=12, message=FALSE, warning=FALSE}
ti3 <- tables_proportion_ft(xi = i3$pre$x, 
                              ni = i3$pre$n,
                              analysis = i3)

plot_individual_proportion_ft(words = ti3$b,
                              numbers = ti3$c,
                              sizebox = 0.012,
                              box_ma_results = i3$ma,
                              overall_box = 1.5)
```
</p>
</details>


<details><summary> Suppl. Figure 12: (FT) Frequency of Incidental imaging diagnosis in Female patients with TC </summary>
<p>
```{r ft_imaging_female, echo=FALSE, fig.height=3, fig.width=12, message=FALSE, warning=FALSE}
ti5 <- tables_proportion_ft(xi = i5$pre$x, 
                              ni = i5$pre$n,
                              analysis = i5)

plot_individual_proportion_ft(words = ti5$b,
                              numbers = ti5$c,
                              sizebox = 0.012,
                              box_ma_results = i5$ma,
                              overall_box = 1.5)
```
</p>
</details>


<details><summary> Suppl. Figure 13: (FT) Frequency of Incidental imaging diagnosis in patients with TC and  tumor size >10mm </summary>
<p>
```{r ft_imaging_greater10, echo=FALSE, fig.height=3, fig.width=12, message=FALSE, warning=FALSE}
ti11 <- tables_proportion_ft(xi = i11$pre$x, 
                              ni = i11$pre$n,
                              analysis = i11,
                              tumorsize = TRUE)

plot_individual_proportion_ft(words = ti11$b,
                              numbers = ti11$c,
                              sizebox = 0.040,
                              box_ma_results = i11$ma,
                              overall_box = 1)
```
</p>
</details>

  
<details><summary> Suppl. Figure 14: (FT) Frequency of Incidental imaging diagnosis in patients with TC and tumor size <10mm </summary>
<p>
```{r ft_imaging_less10, echo=FALSE, fig.height=3, fig.width=12, message=FALSE, warning=FALSE}
ti13 <- tables_proportion_ft(xi = i13$pre$x, 
                              ni = i13$pre$n,
                              analysis = i13,
                              tumorsize = TRUE)

plot_individual_proportion_ft(words = ti13$b,
                              numbers = ti13$c,
                              sizebox = 0.025,
                              box_ma_results = i13$ma,
                              overall_box = 1)
```
</p>
</details>


<details><summary> Suppl. Figure 15: (FT) Frequency of Incidental imaging diagnosis in patients with TC from the USA </summary>
<p>
```{r ft_imaging_USA, echo=FALSE, fig.height=3, fig.width=12, message=FALSE, warning=FALSE}
ti15 <- tables_proportion_ft(xi = i15$pre$x, 
                              ni = i15$pre$n,
                              analysis = i15)

plot_individual_proportion_ft(words = ti15$b,
                              numbers = ti15$c,
                              sizebox = 0.030,
                              box_ma_results = i15$ma,
                              overall_box = 1)
```
</p>
</details>


<details><summary> Suppl. Figure 16: (FT) Frequency of Incidental imaging diagnosis in patients with TC from a non-USA country </summary>
<p>
```{r ft_imaging_nonUSA, echo=FALSE, fig.height=3, fig.width=12, message=FALSE, warning=FALSE}
ti17 <- tables_proportion_ft(xi = i17$pre$x, 
                              ni = i17$pre$n,
                              analysis = i17)

plot_individual_proportion_ft(words = ti17$b,
                              numbers = ti17$c,
                              sizebox = 0.040,
                              box_ma_results = i17$ma,
                              overall_box = 1)

```
</p>
</details>


<details><summary> Suppl. Figure 17: (FT) Frequency of Incidental imaging diagnosis in patients with TC from population based studies </summary>
<p>
```{r ft_imaging_pop, echo=FALSE, fig.height=3, fig.width=12, message=FALSE, warning=FALSE}
ti19 <- tables_proportion_ft(xi = i19$pre$x, 
                              ni = i19$pre$n,
                              analysis = i19)

plot_individual_proportion_ft(words = ti19$b,
                              numbers = ti19$c,
                              sizebox = 0.015,
                              box_ma_results = i19$ma,
                              overall_box = 1.5)
```
</p>
</details>


<details><summary> Suppl. Figure 18: (FT) Frequency of Incidental imaging diagnosis in patients with TC from non-population-based studies </summary>
<p>
```{r ft_imaging_nonpop, echo=FALSE, fig.height=6, fig.width=12, message=FALSE, warning=FALSE}
ti21 <- tables_proportion_ft(xi = i21$pre$x, 
                              ni = i21$pre$n,
                              analysis = i21)

plot_individual_proportion_ft(words = ti21$b,
                              numbers = ti21$c,
                              sizebox = 0.040,
                              box_ma_results = i21$ma,
                              overall_box = 1.5)
```
</p>
</details>

<br />

> Ultrasound incidental diagnosis


<details><summary> Suppl. Figure 19: (FT) Frequency of Incidental Ultrasound diagnosis in patients with TC </summary>
<p>
```{r ft_ultrasound_overall, echo=FALSE, fig.height=4, fig.width=12, message=FALSE, warning=FALSE} 

tus1 <- tables_proportion_ft(xi = us1$pre$x, 
                              ni = us1$pre$n,
                              analysis = us1)

plot_individual_proportion_ft(words = tus1$b,
                              numbers = tus1$c,
                              sizebox = 0.05,
                              box_ma_results = us1$ma,
                              overall_box = 1)
```
</p>
</details>

<br />

> CT incidental diagnosis

<details><summary> Suppl. Figure 19: (FT) Frequency of Incidental Computed Tomography Scan diagnosis in patients with TC </summary>
<p>
```{r ft_CT_overall, echo=FALSE, fig.height=4, fig.width=12, message=FALSE, warning=FALSE} 

ttac1 <- tables_proportion_ft(xi = tac1$pre$x, 
                              ni = tac1$pre$totalparticipants,
                              analysis = tac1)

plot_individual_proportion_ft(words = ttac1$b,
                              numbers = ttac1$c,
                              sizebox = 0.025,
                              box_ma_results = tac1$ma,
                              overall_box = 1)
```
</p>
</details>


<br />

> PET incidental diagnosis

<details><summary> Suppl. Figure 20: (FT) Frequency of Incidental Positron Emission Tomography diagnosis in patients with TC </summary>
<p>
```{r ft_pet_overall, echo=FALSE, fig.height=4, fig.width=12, message=FALSE, warning=FALSE} 

tpet1 <- tables_proportion_ft(xi = pet1$pre$x, 
                              ni = pet1$pre$n,
                              analysis = pet1)

plot_individual_proportion_ft(words = tpet1$b,
                              numbers = tpet1$c,
                              sizebox = 0.025,
                              box_ma_results = pet1$ma,
                              overall_box = 1)
```
</p>
</details>



<br />

> MRI incidental diagnosis


<details><summary> Suppl. Figure 21: (FT) Frequency of Incidental Magnetic Resonance Imaging diagnosis in patients with TC </summary>
<p>
```{r ft_mri_overall, echo=FALSE, fig.height=4, fig.width=12, message=FALSE, warning=FALSE} 

tmri1 <- tables_proportion_ft(xi = mri1$pre$x, 
                              ni = mri1$pre$n,
                              analysis = mri1)

plot_individual_proportion_ft(words = tmri1$b,
                              numbers = tmri1$c,
                              sizebox = 0.025,
                              box_ma_results = mri1$ma,
                              overall_box = 1)
```
</p>
</details>


<br />

> Histology incidental diagnosis

<details><summary> Suppl. Figure 22: (FT) Frequency of Incidental histology diagnosis in patients with TC </summary>
<p>
```{r ft_histology_overall, echo=FALSE, fig.height=4, fig.width=12, message=FALSE, warning=FALSE}
thist1 <- tables_proportion_ft(xi = hist1$pre$x, 
                              ni = hist1$pre$n,
                              analysis = hist1)

plot_individual_proportion_ft(words = thist1$b,
                              numbers = thist1$c,
                              sizebox = 0.05,
                              box_ma_results = hist1$ma,
                              overall_box = 1.5)
```
</p>
</details>


<details><summary> Suppl. Figure 23: (FT) Frequency of Incidental histology diagnosis in Male patients with TC </summary>
<p>
```{r ft_histology_male, echo=FALSE, fig.height=4, fig.width=12, message=FALSE, warning=FALSE}
thist3 <- tables_proportion_ft(xi = hist3$pre$x, 
                              ni = hist3$pre$n,
                              analysis = hist3)

plot_individual_proportion_ft(words = thist3$b,
                              numbers = thist3$c,
                              sizebox = 0.025,
                              box_ma_results = hist3$ma,
                              overall_box = 1.5)
```
</p>
</details>


<details><summary> Suppl. Figure 24: (FT) Frequency of Incidental Histology diagnosis in Female patients with TC </summary>
<p>
```{r ft_histology_female, echo=FALSE, fig.height=3, fig.width=12, message=FALSE, warning=FALSE}
thist5 <- tables_proportion_ft(xi = hist5$pre$x, 
                              ni = hist5$pre$n,
                              analysis = hist5)

plot_individual_proportion_ft(words = thist5$b,
                              numbers = thist5$c,
                              sizebox = 0.025,
                              box_ma_results = hist5$ma,
                              overall_box = 1.5)
```
</p>
</details>


<details><summary> Suppl. Figure 25: (FT) Frequency of Incidental Histology diagnosis in patients with TC and  tumor size >10mm </summary>
<p>
```{r ft_histology_greater10, echo=FALSE, fig.height=3, fig.width=12, message=FALSE, warning=FALSE}
thist11 <- tables_proportion_ft(xi = hist11$pre$x, 
                              ni = hist11$pre$n,
                              analysis = hist11,
                              tumorsize = TRUE)

plot_individual_proportion_ft(words = thist11$b,
                              numbers = thist11$c,
                              sizebox = 0.025,
                              box_ma_results = hist11$ma,
                              overall_box = 1.5)

```
</p>
</details>

  
<details><summary> Suppl. Figure 26: (FT) Frequency of Incidental Histology diagnosis in patients with TC and tumor size <10mm </summary>
<p>
```{r ft_histidental_less10, echo=FALSE, fig.height=3, fig.width=12, message=FALSE, warning=FALSE}
thist13 <- tables_proportion_ft(xi = hist13$pre$x, 
                              ni = hist13$pre$n,
                              analysis = hist13,
                              tumorsize = TRUE)

plot_individual_proportion_ft(words = thist13$b,
                              numbers = thist13$c,
                              sizebox = 0.025,
                              box_ma_results = hist13$ma,
                              overall_box = 1.5)
```
</p>
</details>


<details><summary> Suppl. Figure 27: (FT) Frequency of Incidental Histology diagnosis in patients with TC from the USA </summary>
<p>
```{r ft_histology_USA, echo=FALSE, fig.height=3, fig.width=12, message=FALSE, warning=FALSE}
thist15 <- tables_proportion_ft(xi = hist15$pre$x, 
                              ni = hist15$pre$n,
                              analysis = hist15)

plot_individual_proportion_ft(words = thist15$b,
                              numbers = thist15$c,
                              sizebox = 0.025,
                              box_ma_results = hist15$ma,
                              overall_box = 1)
```
</p>
</details>


<details><summary> Suppl. Figure 28: (FT) Frequency of Incidental Histology diagnosis in patients with TC from a non-USA country </summary>
<p>
```{r ft_histology_nonUSA, echo=FALSE, fig.height=3, fig.width=12, message=FALSE, warning=FALSE}
thist17 <- tables_proportion_ft(xi = hist17$pre$x, 
                              ni = hist17$pre$n,
                              analysis = hist17)

plot_individual_proportion_ft(words = thist17$b,
                              numbers = thist17$c,
                              sizebox = 0.040,
                              box_ma_results = hist17$ma,
                              overall_box = 1)

```
</p>
</details>


<details><summary> Suppl. Figure 29: (FT) Frequency of Incidental Histology diagnosis in patients with TC from population based studies </summary>
<p>
```{r ft_histology_pop, echo=FALSE, fig.height=3, fig.width=12, message=FALSE, warning=FALSE}
thist19 <- tables_proportion_ft(xi = hist19$pre$x, 
                              ni = hist19$pre$n,
                              analysis = hist19)

plot_individual_proportion_ft(words = thist19$b,
                              numbers = thist19$c,
                              sizebox = 0.0125,
                              box_ma_results = hist19$ma,
                              overall_box = 1)
```
</p>
</details>


<details><summary> Suppl. Figure 30: (FT) Frequency of Incidental Histology diagnosis in patients with TC from non-population-based studies </summary>
<p>
```{r ft_histology_nonpop, echo=FALSE, fig.height=6, fig.width=12, message=FALSE, warning=FALSE}
thist21 <- tables_proportion_ft(xi = hist21$pre$x, 
                              ni = hist21$pre$n,
                              analysis = hist21)

plot_individual_proportion_ft(words = thist21$b,
                              numbers = thist21$c,
                              sizebox = 0.040,
                              box_ma_results = hist21$ma,
                              overall_box = 1)
```
</p>
</details>





## Suppl. Figures using Generalized linear mixed models (GLMM) analysis 

<br />

> Overall incidental diagnosis

<details><summary> Suppl. Figure 31: (GLMM) Frequency of Incidental diagnosis in patients with TC </summary>
<p>
```{r glmm_incidental_overall, echo=FALSE, fig.height=6, fig.width=12, message=FALSE, warning=FALSE} 

tinc2 <- tables_proportion_glmm(xi = inc2$pre$x, 
                              ni = inc2$pre$n,
                              analysis = inc2)

plot_individual_proportion_glmm(words = tinc2$b,
                              numbers = tinc2$c,
                              ind_box = 0.5,
                              overall_box = 1)
```
</p>
</details>


<details><summary> Suppl. Figure 32: (GLMM) Frequency of Incidental diagnosis in Male patients with TC </summary>
<p>
```{r glmm_incidental_male, echo=FALSE, fig.height=4, fig.width=12, message=FALSE, warning=FALSE}
tinc4 <- tables_proportion_glmm(xi = inc4$pre$x, 
                              ni = inc4$pre$n,
                              analysis = inc4)

plot_individual_proportion_glmm(words = tinc4$b,
                              numbers = tinc4$c,
                              ind_box = 0.5,
                              overall_box = 1)
```
</p>
</details>


<details><summary> Suppl. Figure 33: (GLMM) Frequency of Incidental diagnosis in Female patients with TC </summary>
<p>
```{r glmm_incidental_female, echo=FALSE, fig.height=3, fig.width=12, message=FALSE, warning=FALSE}
tinc6 <- tables_proportion_glmm(xi = inc6$pre$x, 
                              ni = inc6$pre$n,
                              analysis = inc6)

plot_individual_proportion_glmm(words = tinc6$b,
                              numbers = tinc6$c,
                              ind_box = 0.5,
                              overall_box = 1)
```
</p>
</details>


<details><summary> Suppl. Figure 34: (GLMM) Frequency of Incidental diagnosis in patients with TC and  tumor size >10mm </summary>
<p>
```{r glmm_incidental_greater10, echo=FALSE, fig.height=3, fig.width=12, message=FALSE, warning=FALSE}
tinc12 <- tables_proportion_glmm(xi = inc12$pre$x, 
                              ni = inc12$pre$n,
                              analysis = inc12,
                              tumorsize = TRUE)

plot_individual_proportion_glmm(words = tinc12$b,
                              numbers = tinc12$c,
                              ind_box = 0.5,
                              overall_box = 1)
```
</p>
</details>

  
<details><summary> Suppl. Figure 35: (GLMM) Frequency of Incidental diagnosis in patients with TC and tumor size <10mm </summary>
<p>
```{r glmm_incidental_less10, echo=FALSE, fig.height=3, fig.width=12, message=FALSE, warning=FALSE}
tinc14 <- tables_proportion_glmm(xi = inc14$pre$x, 
                              ni = inc14$pre$n,
                              analysis = inc14,
                              tumorsize = TRUE)

plot_individual_proportion_glmm(words = tinc14$b,
                              numbers = tinc14$c,
                              ind_box = 0.5,
                              overall_box = 1)
```
</p>
</details>


<details><summary> Suppl. Figure 36: (GLMM) Frequency of Incidental diagnosis in patients with TC from the USA </summary>
<p>
```{r glmm_incidental_USA, echo=FALSE, fig.height=3, fig.width=12, message=FALSE, warning=FALSE}
tinc16 <- tables_proportion_glmm(xi = inc16$pre$x, 
                              ni = inc16$pre$n,
                              analysis = inc16)

plot_individual_proportion_glmm(words = tinc16$b,
                              numbers = tinc16$c,
                              ind_box = 0.5,
                              overall_box = 1)
```
</p>
</details>


<details><summary> Suppl. Figure 37: (GLMM) Frequency of Incidental diagnosis in patients with TC from a non-USA country </summary>
<p>
```{r glmm_incidental_nonUSA, echo=FALSE, fig.height=3, fig.width=12, message=FALSE, warning=FALSE}
tinc18 <- tables_proportion_glmm(xi = inc18$pre$x, 
                              ni = inc18$pre$n,
                              analysis = inc18)

plot_individual_proportion_glmm(words = tinc18$b,
                              numbers = tinc18$c,
                              ind_box = 0.5,
                              overall_box = 1)

```
</p>
</details>


<details><summary> Suppl. Figure 38: (GLMM) Frequency of Incidental diagnosis in patients with TC from population based studies </summary>
<p>
```{r glmm_incidental_pop, echo=FALSE, fig.height=3, fig.width=12, message=FALSE, warning=FALSE}
tinc20 <- tables_proportion_glmm(xi = inc20$pre$x, 
                              ni = inc20$pre$n,
                              analysis = inc20)

plot_individual_proportion_glmm(words = tinc20$b,
                              numbers = tinc20$c,
                              ind_box = 0.5,
                              overall_box = 1)
```
</p>
</details>


<details><summary> Suppl. Figure 39: (GLMM) Frequency of Incidental diagnosis in patients with TC from non-population-based studies </summary>
<p>
```{r glmm_incidental_nonpop, echo=FALSE, fig.height=6, fig.width=12, message=FALSE, warning=FALSE}
tinc22 <- tables_proportion_glmm(xi = inc22$pre$x, 
                              ni = inc22$pre$n,
                              analysis = inc22)

plot_individual_proportion_glmm(words = tinc22$b,
                              numbers = tinc22$c,
                              ind_box = 0.5,
                              overall_box = 1)
```
</p>
</details>


<br />

> Imaging incidental diagnosis


<details><summary> Suppl. Figure 40: (GLMM) Frequency of Incidental diagnosis in patients with TC </summary>
<p>
```{r glmm_imaging_overall, echo=FALSE, fig.height=4, fig.width=12, message=FALSE, warning=FALSE} 

ti2 <- tables_proportion_glmm(xi = i2$pre$x, 
                              ni = i2$pre$n,
                              analysis = i2)

plot_individual_proportion_glmm(words = ti2$b,
                              numbers = ti2$c,
                              ind_box = 0.5,
                              overall_box = 1)
```
</p>
</details>


<details><summary> Suppl. Figure 41: (GLMM) Frequency of Incidental imaging diagnosis in Male patients with TC </summary>
<p>
```{r glmm_imaging_male, echo=FALSE, fig.height=4, fig.width=12, message=FALSE, warning=FALSE}
ti4 <- tables_proportion_glmm(xi = i4$pre$x, 
                              ni = i4$pre$n,
                              analysis = i4)

plot_individual_proportion_glmm(words = ti4$b,
                              numbers = ti4$c,
                              ind_box = 0.5,
                              overall_box = 1.5)
```
</p>
</details>


<details><summary> Suppl. Figure 42: (GLMM) Frequency of Incidental imaging diagnosis in Female patients with TC </summary>
<p>
```{r glmm_imaging_female, echo=FALSE, fig.height=3, fig.width=12, message=FALSE, warning=FALSE}
ti6 <- tables_proportion_glmm(xi = i6$pre$x, 
                              ni = i6$pre$n,
                              analysis = i6)

plot_individual_proportion_glmm(words = ti6$b,
                              numbers = ti6$c,
                              ind_box = 0.5,
                              overall_box = 1.5)
```
</p>
</details>


<details><summary> Suppl. Figure 43: (GLMM) Frequency of Incidental imaging diagnosis in patients with TC and  tumor size >10mm </summary>
<p>
```{r glmm_imaging_greater10, echo=FALSE, fig.height=3, fig.width=12, message=FALSE, warning=FALSE}
ti12 <- tables_proportion_glmm(xi = i12$pre$x, 
                              ni = i12$pre$n,
                              analysis = i12,
                              tumorsize = TRUE)

plot_individual_proportion_glmm(words = ti12$b,
                              numbers = ti12$c,
                              ind_box = 0.5,
                              overall_box = 1.5)
```
</p>
</details>

  
<details><summary> Suppl. Figure 44: (GLMM) Frequency of Incidental imaging diagnosis in patients with TC and tumor size <10mm </summary>
<p>
```{r glmm_imaging_less10, echo=FALSE, fig.height=3, fig.width=12, message=FALSE, warning=FALSE}
ti14 <- tables_proportion_glmm(xi = i14$pre$x, 
                              ni = i14$pre$n,
                              analysis = i14,
                              tumorsize = TRUE)

plot_individual_proportion_glmm(words = ti14$b,
                              numbers = ti14$c,
                              ind_box = 0.5,
                              overall_box = 1.5)
```
</p>
</details>


<details><summary> Suppl. Figure 45: (GLMM) Frequency of Incidental imaging diagnosis in patients with TC from the USA </summary>
<p>
```{r glmm_imaging_USA, echo=FALSE, fig.height=3, fig.width=12, message=FALSE, warning=FALSE}
ti16 <- tables_proportion_glmm(xi = i16$pre$x, 
                              ni = i16$pre$n,
                              analysis = i16)

plot_individual_proportion_glmm(words = ti16$b,
                              numbers = ti16$c,
                              ind_box = 0.5,
                              overall_box = 1)
```
</p>
</details>


<details><summary> Suppl. Figure 46: (GLMM) Frequency of Incidental imaging diagnosis in patients with TC from a non-USA country </summary>
<p>
```{r glmm_imaging_nonUSA, echo=FALSE, fig.height=3, fig.width=12, message=FALSE, warning=FALSE}
ti18 <- tables_proportion_glmm(xi = i18$pre$x, 
                              ni = i18$pre$n,
                              analysis = i18)

plot_individual_proportion_glmm(words = ti18$b,
                              numbers = ti18$c,
                              ind_box = 0.5,
                              overall_box = 1)

```
</p>
</details>


<details><summary> Suppl. Figure 47: (GLMM) Frequency of Incidental imaging diagnosis in patients with TC from population based studies </summary>
<p>
```{r glmm_imaging_pop, echo=FALSE, fig.height=3, fig.width=12, message=FALSE, warning=FALSE}
ti20 <- tables_proportion_glmm(xi = i20$pre$x, 
                              ni = i20$pre$n,
                              analysis = i20)

plot_individual_proportion_glmm(words = ti20$b,
                              numbers = ti20$c,
                              ind_box = 0.5,
                              overall_box = 1)
```
</p>
</details>


<details><summary> Suppl. Figure 48: (GLMM) Frequency of Incidental imaging diagnosis in patients with TC from non-population-based studies </summary>
<p>
```{r glmm_imaging_nonpop, echo=FALSE, fig.height=6, fig.width=12, message=FALSE, warning=FALSE}
ti22 <- tables_proportion_glmm(xi = i22$pre$x, 
                              ni = i22$pre$n,
                              analysis = i22)

plot_individual_proportion_glmm(words = ti22$b,
                              numbers = ti22$c,
                              ind_box = 0.5,
                              overall_box = 1)
```
</p>
</details>


<br />

> Ultrasound incidental diagnosis


<details><summary> Suppl. Figure 49: (GLMM) Frequency of Incidental Ultrasound diagnosis in patients with TC </summary>
<p>
```{r glmm_ultrasound_overall, echo=FALSE, fig.height=4, fig.width=12, message=FALSE, warning=FALSE} 

tus2 <- tables_proportion_glmm(xi = us2$pre$x, 
                              ni = us2$pre$n,
                              analysis = us2)

plot_individual_proportion_glmm(words = tus2$b,
                              numbers = tus2$c,
                              ind_box = 0.5,
                              overall_box = 1)
```
</p>
</details>

<br />

> CT incidental diagnosis

<details><summary> Suppl. Figure 50: (GLMM) Frequency of Incidental Computed Tomography Scan diagnosis in patients with TC </summary>
<p>
```{r glmm_CT_overall, echo=FALSE, fig.height=4, fig.width=12, message=FALSE, warning=FALSE} 

ttac2 <- tables_proportion_glmm(xi = tac2$pre$x, 
                              ni = tac2$pre$totalparticipants,
                              analysis = tac2)

plot_individual_proportion_glmm(words = ttac2$b,
                              numbers = ttac2$c,
                              ind_box = 0.5,
                              overall_box = 1)
```
</p>
</details>


<br />

> PET incidental diagnosis


<details><summary> Suppl. Figure 51: (GLMM) Frequency of Incidental Positron Emission Tomography diagnosis in patients with TC </summary>
<p>
```{r glmm_pet_overall, echo=FALSE, fig.height=4, fig.width=12, message=FALSE, warning=FALSE} 

tpet2 <- tables_proportion_glmm(xi = pet2$pre$x, 
                              ni = pet2$pre$n,
                              analysis = pet2)

plot_individual_proportion_glmm(words = tpet2$b,
                              numbers = tpet2$c,
                              ind_box = 0.5,
                              overall_box = 1.5)
```
</p>
</details>


<br />

> MRI incidental diagnosis

<details><summary> Suppl. Figure 52: (GLMM) Frequency of Incidental Magnetic Resonance Imaging diagnosis in patients with TC </summary>
<p>
```{r glmm_mri_overall, echo=FALSE, fig.height=4, fig.width=12, message=FALSE, warning=FALSE} 

tmri2 <- tables_proportion_glmm(xi = mri2$pre$x, 
                              ni = mri2$pre$n,
                              analysis = mri2)

plot_individual_proportion_glmm(words = tmri2$b,
                              numbers = tmri2$c,
                              ind_box = 0.5,
                              overall_box = 1)
```
</p>
</details>


<br />

> Histology incidental diagnosis

<details><summary> Suppl. Figure 53: (GLMM) Frequency of Incidental histology diagnosis in patients with TC </summary>
<p>
```{r glmm_histology_overall, echo=FALSE, fig.height=4, fig.width=12, message=FALSE, warning=FALSE}
thist2 <- tables_proportion_glmm(xi = hist2$pre$x, 
                              ni = hist2$pre$n,
                              analysis = hist2)

plot_individual_proportion_glmm(words = thist2$b,
                              numbers = thist2$c,
                              ind_box = 0.5,
                              overall_box = 1)
```
</p>
</details>


<details><summary> Suppl. Figure 54: (GLMM) Frequency of Incidental histology diagnosis in Male patients with TC </summary>
<p>
```{r glmm_histology_male, echo=FALSE, fig.height=4, fig.width=12, message=FALSE, warning=FALSE}
thist4 <- tables_proportion_glmm(xi = hist4$pre$x, 
                              ni = hist4$pre$n,
                              analysis = hist4)

plot_individual_proportion_glmm(words = thist4$b,
                              numbers = thist4$c,
                              ind_box = 0.5,
                              overall_box = 1)
```
</p>
</details>


<details><summary> Suppl. Figure 55: (GLMM) Frequency of Incidental Histology diagnosis in Female patients with TC </summary>
<p>
```{r glmm_histology_female, echo=FALSE, fig.height=3, fig.width=12, message=FALSE, warning=FALSE}
thist6 <- tables_proportion_glmm(xi = hist6$pre$x, 
                              ni = hist6$pre$n,
                              analysis = hist6)

plot_individual_proportion_glmm(words = thist6$b,
                              numbers = thist6$c,
                              ind_box = 0.5,
                              overall_box = 1)
```
</p>
</details>


<details><summary> Suppl. Figure 56: (GLMM) Frequency of Incidental Histology diagnosis in patients with TC and  tumor size >10mm </summary>
<p>
```{r glmm_histology_greater10, echo=FALSE, fig.height=3, fig.width=12, message=FALSE, warning=FALSE}
thist12 <- tables_proportion_glmm(xi = hist12$pre$x, 
                              ni = hist12$pre$n,
                              analysis = hist12,
                              tumorsize = TRUE)

plot_individual_proportion_glmm(words = thist12$b,
                              numbers = thist12$c,
                              ind_box = 0.5,
                              overall_box = 1)

```
</p>
</details>

  
<details><summary> Suppl. Figure 57: (GLMM) Frequency of Incidental Histology diagnosis in patients with TC and tumor size <10mm </summary>
<p>
```{r glmm_histidental_less10, echo=FALSE, fig.height=3, fig.width=12, message=FALSE, warning=FALSE}
thist14 <- tables_proportion_glmm(xi = hist14$pre$x, 
                              ni = hist14$pre$n,
                              analysis = hist14,
                              tumorsize = TRUE)

plot_individual_proportion_glmm(words = thist14$b,
                              numbers = thist14$c,
                              ind_box = 0.5,
                              overall_box = 1)
```
</p>
</details>


<details><summary> Suppl. Figure 58: (GLMM) Frequency of Incidental Histology diagnosis in patients with TC from the USA </summary>
<p>
```{r glmm_histology_USA, echo=FALSE, fig.height=3, fig.width=12, message=FALSE, warning=FALSE}
thist16 <- tables_proportion_glmm(xi = hist16$pre$x, 
                              ni = hist16$pre$n,
                              analysis = hist16)

plot_individual_proportion_glmm(words = thist16$b,
                              numbers = thist16$c,
                              ind_box = 0.5,
                              overall_box = 1)
```
</p>
</details>


<details><summary> Suppl. Figure 59: (GLMM) Frequency of Incidental Histology diagnosis in patients with TC from a non-USA country </summary>
<p>
```{r glmm_histology_nonUSA, echo=FALSE, fig.height=3, fig.width=12, message=FALSE, warning=FALSE}
thist18 <- tables_proportion_glmm(xi = hist18$pre$x, 
                              ni = hist18$pre$n,
                              analysis = hist18)

plot_individual_proportion_glmm(words = thist18$b,
                              numbers = thist18$c,
                              ind_box = 0.5,
                              overall_box = 1)

```
</p>
</details>


<details><summary> Suppl. Figure 60: (GLMM) Frequency of Incidental Histology diagnosis in patients with TC from population based studies </summary>
<p>
```{r glmm_histology_pop, echo=FALSE, fig.height=3, fig.width=12, message=FALSE, warning=FALSE}
thist20 <- tables_proportion_glmm(xi = hist20$pre$x, 
                              ni = hist20$pre$n,
                              analysis = hist20)

plot_individual_proportion_glmm(words = thist20$b,
                              numbers = thist20$c,
                              ind_box = 0.5,
                              overall_box = 1)
```
</p>
</details>


<details><summary> Suppl. Figure 61: (GLMM) Frequency of Incidental Histology diagnosis in patients with TC from non-population-based studies </summary>
<p>
```{r glmm_histology_nonpop, echo=FALSE, fig.height=4, fig.width=12, message=FALSE, warning=FALSE}
thist22 <- tables_proportion_glmm(xi = hist22$pre$x, 
                              ni = hist22$pre$n,
                              analysis = hist22)

plot_individual_proportion_glmm(words = thist22$b,
                              numbers = thist22$c,
                              ind_box = 0.5,
                              overall_box = 1)
```
</p>
</details>






